Proposed Solution

### 2016-11-10 Ennan-Proposal/travis.tex
autocommit

The current design of \app does not have any assumptions on whether the
configuration files in the training sets are correct or 
incorrect, thus making \app more general and practical.
Nevertheless, some cases in practice 
may allow us to assume some of configuration 
files in the training sets are guaranteed to be correct.
For example, TravisCI is a famous system connected 
to Github, and it allows programmers to automatically run 
their test suites on every code commit. 
Thus, a TravisCI user needs to add a configuration file 
to the repository that 
enables TravisCI and specifies build conditions, 
such as which dependencies are required, 
and a set of benchmarks to test. This ensures 
the tool to be automatically built correctly on a fresh machine.
Such a configuration file management scheme, in fact, guarantees 
the configuration file versions in the commit history to be 
correct -- otherwise, TravisCI should not work correctly in the past.
\ennan{Need one or two sentences to describe TravisCI misconfiguration
problem is important.}

Driven by the above motivating example, 
we propose an extension to \app that
learns a given training set with pre-knowledge that 
this training set contains some configuration files 
guaranteed to be correct.
Such an extension employs a new algorithm, named version space learning,
to significantly decrease the false positive rate while maintaining 
the detection capability of \app.

\subsection{Version Space For Verification}

Version space learning builds a logical constraint model for binary
classification, which we use to test a configuration file for membership
in the set of all correct files~\cite{mitchell82}.
Traditional version space learning builds a model that tests membership
using a series of disjunctions from a set of predefined hypotheses.
In the extended \app, rather than describing a correct file by allowable 
traits, we describe the required traits. 
This way, our system can not only flag misconfigurations, 
but also give the points of failure for non-membership.
We now show in detail how this process works.

Our definition of a configuration file, $C$, is a file that can be
transformed to an ordered list of $(keyword, value)$ pairs, called
$Line$s. \app builds a model for a single file, $M(C)$, 
that is the set of all possible relations between the lines in the file.
A relation is described by user provided templates.
A template is a function taking some number of lines and determining 
a relation on the keywords of 
the lines ($Line^{n} \rightarrow Rel_{k1,..,kn}$).
For example, we may derive the relation \texttt{extension mysql.so} comes before \texttt{extension recode.so} by using the ordering template.
ConfigC features the following default templates.

\begin{center}
\begin{tabular} {|c|c|c|}
 \hline
 Template & Input  & Relation \\
\hline
\hline
 ordering & (Line,Line) & Before $\vert$ After $\vert$ None \\
 \hline
 integer relation & (Line,Line)  & $< | == | >$  \\
\hline
 type & (Line,Line)  & String $\vert$ Int $\vert$ Filepath $\vert$ IP  \\
\hline
 missing entry & (Line,Line) & Required $\vert$ Not \\
\hline
\end{tabular}
\end{center}

It is assumed if a file is correct, all relations in that file are in the set of necessary relations for any other file to be correct ($Correct(C) \implies \forall r \in M(C), r \in Nec$).
In this way, the initial model is built by creating the strongest conditions for a correct file, called the \textit{specific boundary} in version space learning.
This model is then iteratively relaxed as more examples are seen, a process called \textit{candidate elimination}.
Since we maintain the strongest condition for correctness, this approach will identify many correct files as incorrect, which we call a high false positive rate.
This is a problem when a user is then asked to manually review many files for errors, when the files are in fact correct.

\subsection{Learning From Temporal Properties}

%ConfigC can provide justifications, but has a high false positive rate.
%However, ConfigC only analyzes correct configuration files, and does not consider any ordering between these correct files.
We now present a new algorithm to decrease the false positive rate 
by learning on both correct and incorrect examples, 
as well as temporal structure of these examples.
This extension will build a logical formula representing the entire 
history of examples, and use an SMT solver to find a classification model.

Since a configuration file (\eg, TravisCI configuration file) is dependent
on the code it is trying to build, 
we must consider a more general sense of configuration file.
We will call this a program summary $P_t$, which is a representation 
of the repository which contains the information 
relevant to the learning process.
The subscript on $P_t$ is a timestamp tag based on 
the ordered git commit history.
In the case of TravisCI, this include the \verb|.travis.yml| file, 
as well as code features that may effect build status, 
such as programming language and a list of imported libraries.
The summary must be \textit{sufficiently detailed}, that is it must contain every piece of information that might lead to a build error.

@@

We then can combine Eq \ref{eq:E}, \ref{eq:P}, and \ref{eq:PE} with
conjunctions and ask a SMT solver for a model satisfying the formula.
The resulting model will be the sets $Nec$, and $Br$, which can be used to check new configuration files.
Since we used a similar model to \app, we will still be able to provide justifications for the classification results.

>>>>

The current design of \app does not have any assumptions on whether the
configuration files in the training sets are correct or 
incorrect, thus making \app more general and practical.
We show in Sec~\ref{sec:correctExten} how adding set of known correct files to 
the learning process can improve the false positive rate.
In fact, we occasionally have a training set labelled as both correct and incorrect files.
Furthermore, such a training set may have more embedded information that can be leveraged, such as temporal structure.
Temporal structure in training sets is available when code has a change history, such as in version control.

One such example of such a training set of configuration files is TravisCI~\cite{travis}.
TravisCI, a popular integration and build testing service connected to Github.
TravisCI allows programmers to automatically run their test suite on a fresh virtual machine every time they commit their code.
A TravisCI user must add a configuration file to the repository that specifies build conditions, 
such as which dependencies are required, and a set of benchmarks to test. 
The results of these tests (indicating either passing, failing, or misconfiguration) 
are saved by TravisCI on a publicly available database~\cite{API}.

TravisCI misconfigurations are important to fix because of the developer time cost. 
In addition to being time consuming to fix, a misconfiguration can cause a test suite to run up to 20 mins, only to report a misconfiguration~\cite{API}.
The developer will need to wait to get such a report back to begin even identifying the error.

Driven by the above motivating example, we propose an extension to \app that
learns over a training set with both correct and incorrect examples, as well as a temporal structure.
Such an extension employs an existing technique from the machine learning community, called version space learning,
to significantly decrease the false positive rate while maintaining the detection capability of \app.

\subsection{Version Space Learning with Temporal Properties}

Version space learning builds a logical constraint model for binary
classification~\cite{mitchell82}, which we use to test a configuration file for membership
in the set of all correct files~.
Traditional version space learning builds a model that tests membership
using a series of disjunctions from a set of predefined hypotheses.
Here we will instead use a conjuctions to convey that a configuration file must meet the learned criteria.
This extension will build a logical formula representing the entire 
history of examples, and use an SMT solver to find a classification model.

Since a TravisCI configuration file is dependent
on the code and system it is trying to build, 
we must consider a more general sense of configuration file.
We will call this a program summary $P_t$, which is a representation 
of the repository which contains the information 
relevant to the learning process.
The subscript on $P_t$ is a timestamp tag based on 
the ordered git commit history.
In the case of TravisCI, this include the \verb|.travis.yml| file, 
as well as code features that may effect build status, 
such as programming language and a list of imported libraries.
The summary must be \textit{sufficiently detailed}, that is it must contain every piece of information that might lead to a build error.

@@

We then can combine Eq \ref{eq:E}, \ref{eq:P}, and \ref{eq:PE} with
conjunctions and ask a SMT solver for a model satisfying the formula.
The resulting model will be the sets of necessary rules ($Nec$), and the set of breaking rules ($Br$), which can be used to check new configuration files.
Since we used a similar model to \app, we will still be able to provide justifications for the classification results.
